### 2018-09-02 sections/data_presel.tex
toronto textual part 2

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to give maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold 
with looser identification criteria and no isolation requirement.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

@@

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking period). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both channels, at least three jets and exactly one $b$-tagged jet are required.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and sub-leading $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

Single-electron and single-muon triggers with low $\pt$ threshold and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers without isolation requirements to ensure maximum efficiency. 
For muon triggers, the lowest $\pt$ threshold is 20 (26)~\gev\ in 2015 (2016), while the higher $\pt$ threshold is 50~\gev\ in both years. 
For electrons, triggers with a $\pt$ threshold of 24 (26)~\gev\ in 2015 (2016) and isolation requirements are used
along with triggers with a 60~\gev\ threshold and no isolation requirement, and with a 120 (140)~\gev\ threshold 
with looser identification criteria and no isolation requirement.
For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
In both searches, events satisfying the trigger selection are required to have at least one primary vertex candidate.

@@

In the $\Htautau$ search, events are classified into $\lephad$ and $\hadhad$ channels depending on the 
multiplicity of selected leptons. Events in the $\lephad$ channel are recorded with a single-electron or single-muon trigger 
and are required to have exactly one selected electron or muon and at least one $\tauhad$ candidate. 
The selected light lepton (electron or muon) is required to match, with $\Delta R < 0.15$, the lepton reconstructed by 
the trigger and to have a $\pt$ exceeding the trigger $\pt$ threshold by 1~\gev\ or 2~\gev\ (depending on the lepton trigger and 
data taking conditions). In addition, its electric charge is required to be of opposite sign to that of the leading $\tauhad$ candidate.
Events in the $\hadhad$ channel are recorded with a ditau trigger, and are required to have at least two $\tauhad$ candidates and 
no selected light leptons. The two leading $\tauhad$ candidates are required to have a charge of opposite sign. 
In addition, in both channels, at least three jets and exactly one $b$-tagged jet are required.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{l|c|cc}
\toprule\toprule
\multicolumn{4}{c}{Preselection requirements} \\      
\midrule
Requirement &  $\Hbb$ search & \multicolumn{2}{c}{$\Htautau$ search} \\      
& & $\lephad$ channel & $\hadhad$ channel \\
\midrule
Trigger & single-lepton trigger & single-lepton trigger & ditau trigger  \\
Light leptons  & =1 isolated $e$ or $\mu$ & =1 isolated $e$ or $\mu$ & no isolated $e$ or $\mu$ \\
Tau leptons & -- & $\geq$1 $\tauhad$ & $\geq$2 $\tauhad$ \\
Electric charge ($q$) & -- & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$4 jets & $\geq$3 jets & $\geq$3 jets \\
$b$-tagging & $\geq$2 $b$-tagged jets & =1 $b$-tagged jets & =1 $b$-tagged jets  \\
\bottomrule\bottomrule
\end{tabular}
\caption{\small{Summary of preselection requirements for the $\Hbb$ and $\Htautau$ searches. 
The leading and trailing $\tauhad$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2018-09-02 sections/signal_background_modeling.tex
toronto textual part 2

The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
Parton shower, hadronisation, and underlying event are modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5f FFN~\cite{Ball:2012cx} PDF sets.

@@

Samples of single-top-quark events corresponding to the $t$-channel production mechanism are generated with the 
{\powheg}~v1~\cite{Frederix:2012dh} generator that uses the 4F scheme  for the NLO matrix element calculations
and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
Samples corresponding to the $tW$- and $s$-channel production mechanisms are generated 
with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states are avoided by using 
the ``diagram removal'' scheme~\cite{Frixione:2005vw}.
The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428 with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
sections~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.

@@

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

>>>>

The nominal sample used to model the $\ttbar$ background is generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, is set to 1.5 times the top quark mass. 
Parton shower, hadronisation, and underlying event are modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}, 
and using the MSTW 2008 NNLO~\cite{Martin:2009iq,Martin:2009bu} PDF set. 
The theoretical uncertainties result from variations of the factorisation and renormalisation scales, as well as from uncertainties in the
top quark mass, and in the PDF and $\alpha_{\textrm{S}}$. The latter two represent the largest contribution to the overall theoretical uncertainty 
in the cross section and were calculated using the PDF4LHC prescription~\cite{Botje:2011sn} 
with the MSTW 2008 68\% CL NNLO, CT10 NNLO~\cite{Lai:2010vv,Gao:2013xoa} and NNPDF2.3 5F FFN~\cite{Ball:2012cx} PDF sets.

@@

Samples of single-top-quark events corresponding to the $t$-channel production mechanism are generated with the 
{\powheg}~v1~\cite{Frederix:2012dh} generator that uses the 4F scheme  for the NLO matrix element calculations
and the fixed 4F \textsc{CT10}f\textsc{4}~\cite{Lai:2010vv} PDF set.
Samples corresponding to the $tW$- and $s$-channel production mechanisms are generated 
with {\powheg}~v1 using the CT10 PDF set. Overlaps between the $\ttbar$ and $tW$ final states are avoided by using 
the ``diagram removal'' scheme~\cite{Frixione:2005vw}.
The parton shower, hadronisation and the underlying event are modelled using {\pythia}~6.428~\cite{Sjostrand:2006za} 
with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set 
in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
sections~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.

@@

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pile-up, events from minimum-bias interactions are generated using the {\pythia}~8.186~\cite{Sjostrand:2007gs} 
event generator and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events are processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
is adopted for some of the samples.
% used to estimate systematic uncertainties.
Simulated events are processed through the same reconstruction software as the data, and corrections are applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

### 2018-09-02 sections/strategy_Hbb.tex
toronto textual part 2

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
can be effectively exploited to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity spectrum,
with a very small fraction of events having four or more $b$-tagged jets.

>>>>

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
can be effectively exploited to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging operating point, characterised by a low mistag rate for
charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
with a very small fraction of events having four or more $b$-tagged jets.

### 2018-09-02 sections/strategy_Htautau.tex
toronto textual part 2

Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination
performance of the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:

>>>>

Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.

A large set of potential variables was investigated in each SR separately, and only those variables that led to an improved discrimination
performance of the BDT were kept.  The BDT input variables in each SR are listed in Table~\ref{tab:mva_var} and defined in the following:
